Security on Networks

### 2013-05-14 paper/paper.tex
working on FPTAS for Karger.

@@

>>>>

In fact, there are provable bounds on how good our Monte Carlo results are for the approximation of $\tilde{P}_i$, given by Karp and Luby (1985) for the All Terminal problem (but can easily be extended to our problem):\footnote{See \url{http://www.sciencedirect.com/science/article/pii/0885064X85900214} for the full proof.}

\begin{theorem}
  To estimate the probability $\tilde{P}_i$ for $i \in V \setminus u$ where $u \in V$ is the source node of the infection to within a multiplicative factor of $1 + \epsilon$ for all $\epsilon \in [0,1]$, it suffices to run the Monte Carlo algorithm for a number of trials given by:
  \begin{eqnarray}
    O \left( \frac{\ln n}{\epsilon^2 \tilde{P}_i} \right)
  \end{eqnarray}
\end{theorem}

@@

\section{Fast FPTAS for Infection Probabilities}

Although the problem of solving for infection probabilities is $\# P$ hard, it is still possible to approximate the probabilities. In fact, Karger (1999) developed a Fully Polynomial Time Approximation Scheme (FPTAS) for solving the all terminal problem, which can be defined as follows: given a graph $G = (V,E)$ and a probability function on the edges $Pr: E \to [0,1]$ of the probability of any edge failing, find the probability that the entire graph remains connected after edge failures occur with probability $Pr(e)$ for each edge $e \in E$.

An FPTAS is an incredibly strong result, as it means that for any $\epsilon > 0$, one can use the FPTAS to approximate the result to within a factor of $1 + \epsilon$ in time polynomial in the inputs and $\epsilon$. Thus, one can get arbitrarily close to the exact result by using a smaller and smaller $\epsilon$, in exchange for a higher running time.

There exists a naive generalization of Karger's FPTAS to the problem of computing all infection probabilities. In this section, we provide an overview of Karger's FPTAS, it's naive generalization to computing multiple-source multiple-sink infection probabilities (MSMSIP), and finally an asymptotically faster FPTAS than the naive algorithm for MSMSIP.

\subsection{Multiple-Source Multiple-Sink Infection Probabilities}

First we define the problem of computing infection probabilities for multiple sources and multiple sinks.

\begin{definition}
    We will be given a graph $G = (V,E)$ and some function of protections $Q: E \to [0,1)$ which defines the protection $q_v$ inherent for the infection to move down edge $(u,v)$. The \emph{MSMSIP problem} is to find the probability of infection $P_i(u)$ for each node $i \in V \setminus u$ for all possible starting nodes $u \in V$.
  \end{definition}

  Since we have shown the single-source single-sink infection probability problem to be $\# P$, it must be the case that MSMSIP is also $\# P$ because solving the MSMSIP implies that you have also solved the singular problem.

\subsection{Summary of Karger's FPTAS for the All Terminal Problem}

Karger solves the all terminal problem using a reduction to D
